---
title: "Annual Production Patterns"
format: 
  html:
    theme: cosmo
    toc: true
    toc-location: left
    css: custom.css
    page-layout: full
    self-contained: true
    fig-width: 8
    fig-height: 8
    fig-format: "png"
    fig-dpi: 300
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width = 4, fig.height = 4, out.width = "75%")
library(knitr)
library(fs)
library(ggplot2)
library(gridExtra)
library(grid)
library(png)
library(patchwork) # For arranging plots

# Create output directory for image copies
output_dir <- "_output_images"
dir_create(output_dir)

# Function to copy an image to the output directory and return the new path
copy_and_get_path <- function(original_path, new_name) {
  # Create the new path
  new_path <- file.path(output_dir, new_name)
  
  # Copy file if it exists
  if (file.exists(original_path)) {
    file_copy(original_path, new_path, overwrite = TRUE)
    return(new_path)
  } else {
    # If file doesn't exist, return NULL
    message("File not found: ", original_path)
    return(NULL)
  }
}

# Function to display an image with error handling and wider display
display_image <- function(path) {
  if (is.null(path) || !file.exists(path)) {
    cat("Image not available")
    return(invisible(NULL))
  }
  
  # Set a wider image
  include_graphics(path, dpi = 300)
}
```

## Overview

These maps show:

- **Production per km**: Relative production scaled by stream length in each HUC subwatershed
- **Raw production**: Total proportion of production in each area (unscaled)
- **Tributary patterns**: Stream-by-stream production concentrations

# Kuskokwim Watershed

### Management Rivers

Tried my hand at making a better version of the management rivers figure for the Kusko. Needs some work. 

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Figures/Non_production_maps/mngmnt_rivers.png"
new_path <- copy_and_get_path(img_path, "management_rivers.png")
display_image(new_path)
```



## Annual HUC Maps


These maps show the relative production per river kilometer in different subwatersheds.

::: {.panel-tabset}

## 2017

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/HUC/2017_Kusko_HUC8_0.7_StrOrd3_.png"
new_path <- copy_and_get_path(img_path, "kusko_2017_huc.png")
display_image(new_path)
```

## 2018

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/HUC/2018_Kusko_HUC8_0.7_StrOrd3_.png"
new_path <- copy_and_get_path(img_path, "kusko_2018_huc.png")
display_image(new_path)
```

## 2019

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/HUC/2019_Kusko_HUC8_0.7_StrOrd3_.png"
new_path <- copy_and_get_path(img_path, "kusko_2019_huc.png")
display_image(new_path)
```

## 2020

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/HUC/2020_Kusko_HUC8_0.7_StrOrd3_.png"
new_path <- copy_and_get_path(img_path, "kusko_2020_huc.png")
display_image(new_path)
```

## 2021

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/HUC/2021_Kusko_HUC8_0.7_StrOrd3_.png"
new_path <- copy_and_get_path(img_path, "kusko_2021_huc.png")
display_image(new_path)
```

:::

## Raw Production Maps

These maps show the raw proportion of total production in each HUC subwatershed, without adjusting for stream length.

::: {.panel-tabset}

## 2017

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/HUC/RawProduction/2017_Kusko_RawProd_HUC8_0.7_StrOrd3_.png"
new_path <- copy_and_get_path(img_path, "kusko_2017_raw.png")
display_image(new_path)
```

## 2018

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/HUC/RawProduction/2018_Kusko_RawProd_HUC8_0.7_StrOrd3_.png"
new_path <- copy_and_get_path(img_path, "kusko_2018_raw.png")
display_image(new_path)
```

## 2019

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/HUC/RawProduction/2019_Kusko_RawProd_HUC8_0.7_StrOrd3_.png"
new_path <- copy_and_get_path(img_path, "kusko_2019_raw.png")
display_image(new_path)
```

## 2020

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/HUC/RawProduction/2020_Kusko_RawProd_HUC8_0.7_StrOrd3_.png"
new_path <- copy_and_get_path(img_path, "kusko_2020_raw.png")
display_image(new_path)
```

## 2021

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/HUC/RawProduction/2021_Kusko_RawProd_HUC8_0.7_StrOrd3_.png"
new_path <- copy_and_get_path(img_path, "kusko_2021_raw.png")
display_image(new_path)
```

:::

## Tributary Maps

These maps show the concentration of natal origin locations for each tributary in the basin. The stream thickness indicates stream order (larger rivers shown with thicker lines), and colors represent the relative contribution of each tributary to the overall production.

::: {.panel-tabset}

## 2017

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/Tribs/2017_Kusko_0.7_StrOrd3_.png"
new_path <- copy_and_get_path(img_path, "kusko_2017_tribs.png")
display_image(new_path)
```

## 2018

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/Tribs/2018_Kusko_0.7_StrOrd3_.png"
new_path <- copy_and_get_path(img_path, "kusko_2018_tribs.png")
display_image(new_path)
```

## 2019

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/Tribs/2019_Kusko_0.7_StrOrd3_.png"
new_path <- copy_and_get_path(img_path, "kusko_2019_tribs.png")
display_image(new_path)
```

## 2020

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/Tribs/2020_Kusko_0.7_StrOrd3_.png"
new_path <- copy_and_get_path(img_path, "kusko_2020_tribs.png")
display_image(new_path)
```

## 2021

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/Tribs/2021_Kusko_0.7_StrOrd3_.png"
new_path <- copy_and_get_path(img_path, "kusko_2021_tribs.png")
display_image(new_path)
```

:::

# Yukon Watershed

## Annual HUC Maps

These maps show the relative production per river kilometer in different subwatersheds for the Yukon basin.

::: {.panel-tabset}

## 2015

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/HUC/2015_Yukon_HUC8_0.8_StrOrd4_.png"
new_path <- copy_and_get_path(img_path, "yukon_2015_huc.png")
display_image(new_path)
```

## 2016

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/HUC/2016_Yukon_HUC8_0.8_StrOrd4_.png"
new_path <- copy_and_get_path(img_path, "yukon_2016_huc.png")
display_image(new_path)
```

## 2021

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/HUC/2021_Yukon_HUC8_0.8_StrOrd4_.png"
new_path <- copy_and_get_path(img_path, "yukon_2021_huc.png")
display_image(new_path)
```

:::

## Raw Production Maps

These maps show the raw proportion of total production in each HUC subwatershed, without adjusting for stream length.

::: {.panel-tabset}

## 2015

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/HUC/RawProduction/2015_Yukon_RawProd_HUC8_0.8_StrOrd4_.png"
new_path <- copy_and_get_path(img_path, "yukon_2015_raw.png")
display_image(new_path)
```

## 2016

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/HUC/RawProduction/2016_Yukon_RawProd_HUC8_0.8_StrOrd4_.png"
new_path <- copy_and_get_path(img_path, "yukon_2016_raw.png")
display_image(new_path)
```

## 2021

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/HUC/RawProduction/2021_Yukon_RawProd_HUC8_0.8_StrOrd4_.png"
new_path <- copy_and_get_path(img_path, "yukon_2021_raw.png")
display_image(new_path)
```

:::

## Tributary Maps

These maps show the concentration of natal origin locations for each tributary in the Yukon basin. The stream thickness indicates stream order, with larger rivers shown as thicker lines.

::: {.panel-tabset}

## 2015

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/Tribs/2015_Yukon_0.8_StrOrd4_.png"
new_path <- copy_and_get_path(img_path, "yukon_2015_tribs.png")
display_image(new_path)
```

## 2016

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/Tribs/2016_Yukon_0.8_StrOrd4_.png"
new_path <- copy_and_get_path(img_path, "yukon_2016_tribs.png")
display_image(new_path)
```

## 2021

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/Tribs/2021_Yukon_0.8_StrOrd4_.png"
new_path <- copy_and_get_path(img_path, "yukon_2021_tribs.png")
display_image(new_path)
```

:::
