---
title: "Kuskokwim Basin Maps"
format: 
  html:
    theme: cosmo
    toc: true
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, fig.width = 16, fig.height = 10, out.width = "100%")
library(knitr)
library(fs)
library(ggplot2)
library(gridExtra)
library(grid)
library(png)
library(patchwork) # For arranging plots

# Create output directory for image copies
output_dir <- "_output_images"
dir_create(output_dir)

# Function to copy an image to the output directory and return the new path
copy_and_get_path <- function(original_path, new_name) {
  # Create the new path
  new_path <- file.path(output_dir, new_name)
  
  # Copy file if it exists
  if (file.exists(original_path)) {
    file_copy(original_path, new_path, overwrite = TRUE)
    return(new_path)
  } else {
    # If file doesn't exist, return NULL
    message("File not found: ", original_path)
    return(NULL)
  }
}

# Function to display an image with error handling and wider display
display_image <- function(path) {
  if (is.null(path) || !file.exists(path)) {
    cat("Image not available")
    return(invisible(NULL))
  }
  
  # Set a wider image
  include_graphics(path, dpi = 300)
}
```

## Kuskokwim Annual HUC Maps

::: {.panel-tabset}

## 2017

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/HUC/2017_Kusko_HUC8_1e-04_StrOrd3_.png"
new_path <- copy_and_get_path(img_path, "kusko_2017_huc.png")
display_image(new_path)
```

## 2019

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/HUC/2019_Kusko_HUC8_1e-04_StrOrd3_.png"
new_path <- copy_and_get_path(img_path, "kusko_2019_huc.png")
display_image(new_path)
```

## 2020

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/HUC/2020_Kusko_HUC8_1e-04_StrOrd3_.png"
new_path <- copy_and_get_path(img_path, "kusko_2020_huc.png")
display_image(new_path)
```

## 2021

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/HUC/2021_Kusko_HUC8_1e-04_StrOrd3_.png"
new_path <- copy_and_get_path(img_path, "kusko_2021_huc.png")
display_image(new_path)
```

:::

## Kuskokwim Raw Production Maps

::: {.panel-tabset}

## 2017

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/HUC/RawProduction/2017_Kusko_RawProd_HUC8_1e-04_StrOrd3_.png"
new_path <- copy_and_get_path(img_path, "kusko_2017_raw.png")
display_image(new_path)
```

## 2019

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/HUC/RawProduction/2019_Kusko_RawProd_HUC8_1e-04_StrOrd3_.png"
new_path <- copy_and_get_path(img_path, "kusko_2019_raw.png")
display_image(new_path)
```

## 2020

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/HUC/RawProduction/2020_Kusko_RawProd_HUC8_1e-04_StrOrd3_.png"
new_path <- copy_and_get_path(img_path, "kusko_2020_raw.png")
display_image(new_path)
```

## 2021

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/HUC/RawProduction/2021_Kusko_RawProd_HUC8_1e-04_StrOrd3_.png"
new_path <- copy_and_get_path(img_path, "kusko_2021_raw.png")
display_image(new_path)
```

:::

## Kuskokwim Tributary Maps

::: {.panel-tabset}

## 2017

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/Tribs/2017_Kusko_1e-04_StrOrd3_.png"
new_path <- copy_and_get_path(img_path, "kusko_2017_tribs.png")
display_image(new_path)
```

## 2019

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/Tribs/2019_Kusko_1e-04_StrOrd3_.png"
new_path <- copy_and_get_path(img_path, "kusko_2019_tribs.png")
display_image(new_path)
```

## 2020

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/Tribs/2020_Kusko_1e-04_StrOrd3_.png"
new_path <- copy_and_get_path(img_path, "kusko_2020_tribs.png")
display_image(new_path)
```

## 2021

```{r}
img_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Annual_Maps/Tribs/2021_Kusko_1e-04_StrOrd3_.png"
new_path <- copy_and_get_path(img_path, "kusko_2021_tribs.png")
display_image(new_path)
```

:::

## DOY Quartile Analysis

This section shows how salmon production is distributed across different calendar periods (Day of Year quartiles). The composite figures display all years side by side for each quartile.

::: {.panel-tabset}

## Q1 (Early Run)

```{r}
# Get the composite figure for DOY Q1
composite_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Composite_Figures/Kusko/DOY/HUC/Q1_Composite.png"
new_path <- copy_and_get_path(composite_path, "kusko_doy_q1_composite.png")
display_image(new_path)
```

## Q2

```{r}
# Get the composite figure for DOY Q2
composite_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Composite_Figures/Kusko/DOY/HUC/Q2_Composite.png"
new_path <- copy_and_get_path(composite_path, "kusko_doy_q2_composite.png")
display_image(new_path)
```

## Q3

```{r}
# Get the composite figure for DOY Q3
composite_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Composite_Figures/Kusko/DOY/HUC/Q3_Composite.png"
new_path <- copy_and_get_path(composite_path, "kusko_doy_q3_composite.png")
display_image(new_path)
```

## Q4 (Late Run)

```{r}
# Get the composite figure for DOY Q4
composite_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Composite_Figures/Kusko/DOY/HUC/Q4_Composite.png"
new_path <- copy_and_get_path(composite_path, "kusko_doy_q4_composite.png")
display_image(new_path)
```

:::

## DOY Raw Production Quartile Analysis

This section shows the raw production proportion across different parts of the run by Day of Year quartiles.

::: {.panel-tabset}

## Q1 (Early Run)

```{r}
# Get the composite figure for DOY Q1 Raw Production
composite_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Composite_Figures/Kusko/DOY/RawProduction/Q1_Composite.png"
new_path <- copy_and_get_path(composite_path, "kusko_doy_q1_raw_composite.png")
display_image(new_path)
```

## Q2

```{r}
# Get the composite figure for DOY Q2 Raw Production
composite_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Composite_Figures/Kusko/DOY/RawProduction/Q2_Composite.png"
new_path <- copy_and_get_path(composite_path, "kusko_doy_q2_raw_composite.png")
display_image(new_path)
```

## Q3

```{r}
# Get the composite figure for DOY Q3 Raw Production
composite_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Composite_Figures/Kusko/DOY/RawProduction/Q3_Composite.png"
new_path <- copy_and_get_path(composite_path, "kusko_doy_q3_raw_composite.png")
display_image(new_path)
```

## Q4 (Late Run)

```{r}
# Get the composite figure for DOY Q4 Raw Production
composite_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Composite_Figures/Kusko/DOY/RawProduction/Q4_Composite.png"
new_path <- copy_and_get_path(composite_path, "kusko_doy_q4_raw_composite.png")
display_image(new_path)
```

:::

## DOY Tributary Quartile Analysis

This section shows tributary-level production across different parts of the run by Day of Year quartiles.

::: {.panel-tabset}

## Q1 (Early Run)

```{r}
# Get the composite figure for DOY Q1 Tributaries
composite_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Composite_Figures/Kusko/DOY/Tribs/Q1_Composite.png"
new_path <- copy_and_get_path(composite_path, "kusko_doy_q1_tribs_composite.png")
display_image(new_path)
```

## Q2

```{r}
# Get the composite figure for DOY Q2 Tributaries
composite_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Composite_Figures/Kusko/DOY/Tribs/Q2_Composite.png"
new_path <- copy_and_get_path(composite_path, "kusko_doy_q2_tribs_composite.png")
display_image(new_path)
```

## Q3

```{r}
# Get the composite figure for DOY Q3 Tributaries
composite_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Composite_Figures/Kusko/DOY/Tribs/Q3_Composite.png"
new_path <- copy_and_get_path(composite_path, "kusko_doy_q3_tribs_composite.png")
display_image(new_path)
```

## Q4 (Late Run)

```{r}
# Get the composite figure for DOY Q4 Tributaries
composite_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Composite_Figures/Kusko/DOY/Tribs/Q4_Composite.png"
new_path <- copy_and_get_path(composite_path, "kusko_doy_q4_tribs_composite.png")
display_image(new_path)
```

:::

## DOY Cumulative Analysis

This section shows the cumulative progression of salmon production by Day of Year periods.

::: {.panel-tabset}

## Q1 (First 25%)

```{r}
# Get the composite figure for DOY Cumulative Q1
composite_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Composite_Figures/Kusko/Cumulative_DOY/HUC/Q1_Composite.png"
new_path <- copy_and_get_path(composite_path, "kusko_doy_cum_q1_composite.png")
display_image(new_path)
```

## Q2 (First 50%)

```{r}
# Get the composite figure for DOY Cumulative Q2
composite_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Composite_Figures/Kusko/Cumulative_DOY/HUC/Q2_Composite.png"
new_path <- copy_and_get_path(composite_path, "kusko_doy_cum_q2_composite.png")
display_image(new_path)
```

## Q3 (First 75%)

```{r}
# Get the composite figure for DOY Cumulative Q3
composite_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Composite_Figures/Kusko/Cumulative_DOY/HUC/Q3_Composite.png"
new_path <- copy_and_get_path(composite_path, "kusko_doy_cum_q3_composite.png")
display_image(new_path)
```

## Q4 (Full Run)

```{r}
# Get the composite figure for DOY Cumulative Q4
composite_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Composite_Figures/Kusko/Cumulative_DOY/HUC/Q4_Composite.png"
new_path <- copy_and_get_path(composite_path, "kusko_doy_cum_q4_composite.png")
display_image(new_path)
```

:::

## DOY Cumulative Raw Production Analysis

This section shows the cumulative raw production progression by Day of Year periods.

::: {.panel-tabset}

## Q1 (First 25%)

```{r}
# Get the composite figure for DOY Cumulative Q1 Raw Production
composite_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Composite_Figures/Kusko/Cumulative_DOY/RawProduction/Q1_Composite.png"
new_path <- copy_and_get_path(composite_path, "kusko_doy_cum_q1_raw_composite.png")
display_image(new_path)
```

## Q2 (First 50%)

```{r}
# Get the composite figure for DOY Cumulative Q2 Raw Production
composite_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Composite_Figures/Kusko/Cumulative_DOY/RawProduction/Q2_Composite.png"
new_path <- copy_and_get_path(composite_path, "kusko_doy_cum_q2_raw_composite.png")
display_image(new_path)
```

## Q3 (First 75%)

```{r}
# Get the composite figure for DOY Cumulative Q3 Raw Production
composite_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Composite_Figures/Kusko/Cumulative_DOY/RawProduction/Q3_Composite.png"
new_path <- copy_and_get_path(composite_path, "kusko_doy_cum_q3_raw_composite.png")
display_image(new_path)
```

## Q4 (Full Run)

```{r}
# Get the composite figure for DOY Cumulative Q4 Raw Production
composite_path <- "/Users/benjaminmakhlouf/Research_repos/03_Shifting-Habitat-Mosaics-II/Basin Maps/Composite_Figures/Kusko/Cumulative_DOY/RawProduction/Q4_Composite.png"
new_path <- copy_and_get_path(composite_path, "kusko_doy_cum_q4_raw_composite.png")
display_image(new_path)
```

:::